An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-03-14 Paper.tex
Edit text of paper
This commit makes a lot of minor edits to the text of the paper and the math.

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an \textsc{lm} or Wald test, which depend on just the
restricted or unrestricted model respectively.  Simulations presented
in Section~\ref{sec:2} show that this approach gives a substantial
power advantage when there are breaks.

@@

Since researchers often have a set of potential models and want to
know which of them significantly outperform the benchmark, procedures
that compare a single pair of models are of limited practical value.
As \citet{Whi:00} demonstrates, looking at the naive $p$-values of
individual tests is misleading, but researchers can get a valid test
by using the bootstrap to approximate the distribution of the largest
individual test statistic under the null (White calls this procedure
the \textit{Bootstrap Reality Check} or \brc).  This paper presents a test
for equal predictive ability of multiple models based on
\citepos{RoW:05} StepM, which uses a step-down procedure that
iteratively rejects models to achieve higher power than the \brc\ and
indicate which of the models improves on the benchmark (see
Theorem~\ref{res:2} for details).

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\beta_0)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{2}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\beta_0) = \oclt{t} \Big[(y_{t+1} - 
  x_t\beta_0)^2 - (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
the size of the test sample used to evaluate the forecasting models.
\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
$z_{t-R}$ where $z_t$ is another weakly dependent random process),
which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
the weak dependence properties of the variables used to estimate it.
Keeping $R$ finite ensures that the conditional variance remains
positive, so the sum obeys a \clt.  This method of ensuring normality
was introduced by \citet{GiW:06}.  The coefficients $\beta_0$ are
assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
the null hypothesis) and Clark and West propose using this statistic
to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
$\mathcal{F}_t$.  In \citet{ClW:07}, $\beta_0$ is unknown but is
estimated with a fixed-length rolling window as well, so
\begin{equation*}
  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{s-1} x_{s-1}'\Big)^{-1}
  \sum_{s=t-R+1}^t x_{s-1} y_s
\end{equation*}
and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
$\varepsilon_{t+1}$ in the test statistic for \mds.  Unfortunately,
$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
mean-zero normal, even though this approximation performs well in the
simulations reported by \citet{ClW:07}.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\beta_0$ and produce
$\hat{\varepsilon}_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06}, these conditions are ensured if $v_t$ is another
forecast of $y_{t+1}$ based on a fixed length rolling window.
Theorem~\ref{res:1} presents the details of this result.  The
assumptions required are essentially the same in existing papers
(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).  Please see the
original papers for a discussion of these assumptions.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$, $\hat{y}_{1t}$, and $x_t$
    have uniformly bounded $2 r$ moments for some $r > 2$, and $\hat
    y_t y_t$ $\hat y_t x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1},
    x_{t-1}'$ are $L_2$-\ned\ of size $-\frac12$ on a strong mixing
    series of size $-\frac{r}{r-2}$ for $r>2$ or a uniform mixing
    series of size $-\frac{r}{2r-2}$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \osum{t} g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

\begin{rem}
  Forecasters are usually interested in the one-sided alternative that
  $\E f_t(\beta_0) > 0$; i.e. that the alternative model is expected
  to forecast better than the benchmark.
\end{rem}

@@

\begin{rem}
  The requirement that the asymptotic variance of $\bar f(\beta_0)$ be
  uniformly positive is much less restrictive than in \cite{Wes:96}.
  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
  serves to rule out pathological cases---for example, letting both
  the benchmark and the alternative model be white noise. In
  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
  well as the forecasting models, but in this paper it is a
  restriction only on the models.
\end{rem}

@@

\begin{rem}
  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
  and $\hat{S}_{gg}$ with their \hac\ counterparts.
  Lemma~\ref{res:a5} presents a more general version of the theorem
  that can cover this case.
\end{rem}

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  Our statistic can be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.}
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

\begin{rem}
  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize model comparison
  using a rolling window but claim in passing that their results hold
  for a fixed-length fixed window as well, where the unknown
  coefficients are estimated only once using the first $R$
  observations.  This claim is true but not obvious.  The proof for
  the rolling window is based on weak dependence that arises because
  the forecast errors are a function of a finite number of consecutive
  weakly dependent observations.  But using a fixed window introduces
  another source of dependence: all of the forecasts depend on the
  same coefficient estimates and the estimation uncertainty introduced
  by those estimates does not vanish when $R$ is bounded.  One can
  prove that their results apply to fixed window forecasts by using a
  coupling argument similar to \citepos{Cal:11}.  Interested readers
  should refer to \citet{Cal:11} for the argument and to
  \citet{MeP:02} for a review of the necessary coupling results.
  Theorem~\ref{res:1} can be shown to hold when $\hat y_{1t}$ is
  estimated with a fixed-length fixed window using the same arguments.
\end{rem}

Since most empirical papers study more than one alternative model,
Theorem~\ref{sec:1} is of limited use on its own.\footnote{Moreover,
  we would need to account for the existence of multiple models even if
each paper considers a single model, since there are many papers
studying the same data.}  It can, however, be
used as the basis for a procedure that allows researchers to make
multiple comparisons.  Before presenting a theoretical result, I'll
discuss some issues related to multiple hypothesis testing.

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.}  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though the papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:12b} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and can control \sfwe\ as long as there is a
consistent estimator of that distribution.

@@

This procedure exploits the fact that $R$ is finite in
Theorem~\ref{res:1} and that the expected block length will grow with
$T$.  Under these asymptotics, a growing proportion of the
rolling-window forecasts are the same if we bootstrap the forecasts as
if we bootstrap the empirical data and reestimate the models.
Bootstrapping the forecasts makes the computations faster and easier,
but requires us to drop the first $R$ observations from the bootstrap
(the alternative forecasts are not defined for the first $R$
observations).  I add those observations to the beginning of each
bootstrap sample so that population means under the bootstrap-induced
probability distribution equal sample means.  The benchmark model
still needs to be reestimated in each bootstrap sample.

@@

\begin{thm}\label{res:2}
  Suppose the conditions of Theorem~\ref{res:1} hold, with assumptions
  on the alternative model, $\hat{y}_{1t}$, holding for each of the
  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$ and let the subscript
  $l$ denote the different quantities associated with $\hat{y}_{lt}$
  (i.e. $\mathcal{F}_{lt}$, etc.)  Also assume that the long-run
  variance-covariance matrix of the vector
  $(\bar{f}_1(\beta_0),\dots,\bar{f}_m(\beta_0))'$ is uniformly
  positive definite.

>>>>

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a Likelihood Ratio
Test instead of an \textsc{lm} or Wald test, which depend on just the
restricted or unrestricted model respectively.

@@

Since researchers often have a set of potential models and want to
know which of them significantly outperform the benchmark, procedures
that compare a single pair of models are of limited practical value.
As \citet{Whi:00} demonstrates, looking at the naive $p$-values of
individual tests is misleading, but researchers can obtain a valid test
by using the bootstrap to approximate the distribution of the largest
individual test statistic under the null (White calls this procedure
the \textit{Bootstrap Reality Check} or \brc).  This paper presents a test
for equal predictive ability of multiple models based on
\citepos{RoW:05} StepM, which uses a step-down procedure that
iteratively rejects models to achieve higher power than the \brc\ and
indicate which of the models improves on the benchmark (see
Theorem~\ref{res:2} for details).

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I will present the
single-comparison statistic first and then extend it to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudo-true
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is a martingale difference
sequence with respect to $\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t),
(x_{t-1}, v_{t-1}, y_{t-1}),\dots)$, then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
the size of the test sample used to evaluate the forecasting models.
\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
$z_{t-R}$ where $z_t$ is another weakly dependent random process),
which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
the weak dependence properties of the variables used to estimate it.
Keeping $R$ finite ensures that the conditional variance remains
positive, so the sum obeys a \clt.  This method of ensuring normality
was introduced by \citet{GiW:06}.  In \citet{ClW:06}, the coefficients $\btrue$ are
assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
the null hypothesis) and Clark and West propose using this statistic
to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
$\mathcal{F}_t$.  In \citet{ClW:07}, $\btrue$ is unknown but is
estimated with a fixed-length rolling window as well, so
\begin{equation*}
  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{s-1} x_{s-1}'\Big)^{-1}
  \sum_{s=t-R+1}^t x_{s-1} y_s
\end{equation*}
and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
$\varepsilon_{t+1}$ in the test statistic for \mds.  Unfortunately,
$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
mean-zero normal, even though this approximation performs well in the
simulations reported by \citet{ClW:07}.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\btrue$ and produce
$\hat{\varepsilon}_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06}, these conditions are ensured if $v_t$ is another
forecast of $y_{t+1}$ based on a fixed length rolling window.
Theorem~\ref{res:1} presents the details of this result.  The
assumptions required are essentially the same in existing papers
(e.g. \citealp{Wes:96}; \citealp{WeM:98}; \citealp{Mcc:00};
\citealp{GiW:06}; and \citealp{ClW:06,ClW:07}).  Please see the
original papers for a discussion of these assumptions.

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\btrue = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\btrue$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$, $\hat{y}_{1t}$, and $x_t$
    have uniformly bounded $2 r$ moments for some $r > 2$, and $\hat
    y_t y_t$ $\hat y_t x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1},
    x_{t-1}'$ are $L_2$-\ned\ of size $-\frac12$ on a strong mixing
    series of size $-\frac{r}{r-2}$ for $r>2$ or a uniform mixing
    series of size $-\frac{r}{2r-2}$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $f_t = f_t(\beta_0)$, $\hat f_t = f_t(\hat\beta_t)$,
    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} \hat f_t$, with $P = T - R$;
    $\bar f(\btrue)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\btrue)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (\hat f_t - \bar f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (\hat f_t - \bar{f})(\hat g_t - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (\hat g_t - \bar g)(\hat g_t - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \oavg{t}
  \hat g_t$, $\X' = [x_1,\dots,x_T]$,
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta),
  \end{equation*}
  and $\hat g_t = g_t(\hat\beta_t)$.
\end{thm}

@@

\begin{rem}
  Forecasters are usually interested in the one-sided alternative that
  $\E f_t > 0$; i.e. that the alternative model is expected
  to forecast better than the benchmark.
\end{rem}

@@

\begin{rem}
  The requirement that the asymptotic variance of $\bar f(\btrue)$ is
  uniformly positive is much less restrictive than in \cite{Wes:96}.
  As in \cite{GiW:06} and \citet{ClW:06,ClW:07}, the assumption only
  serves to rule out pathological cases---for example, letting both
  the benchmark and the alternative model be perfectly correlated white noise. In
  \citet{Wes:96}, this assumption is a restriction on the \dgp\ as
  well as the forecasting models, but in this paper it is a
  restriction only on the models.
\end{rem}

@@

\begin{rem}
  The statistic we present tests the null hypothesis that the forecast
  errors from the population version of the benchmark model are a
  martingale difference sequence.  This hypothesis may not be
  appropriate, depending on the loss function or utility function of
  interest.  If one wants to test the less restrictive null hypothesis that
  $y_{t} - \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{1t}$ but not
  necessarily an \mds, one can replace $\hat{S}_{ff}$, $\hat{S}_{fg}$
  and $\hat{S}_{gg}$ with their \hac\ counterparts.  
  Our statistic can also be modified to test implications of
  optimal forecasts under other loss functions
  \citep[see][]{PaT:07,PaT:07b}; the statistic should be expressed as
  a forecast encompassing test using the models' generalized forecast
  errors.\footnote{See \citet{HLN:98} and \citet[Section~4]{ClW:07}.}
  Again, Lemma~\ref{res:a5} can cover these other applications.
\end{rem}

\begin{rem}
  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize model comparison
  using a rolling window but claim in passing that their results hold
  for a fixed-length fixed window as well, where the unknown
  coefficients are estimated only once using the first $R$
  observations.  This claim is true but not obvious.  The proof for
  the rolling window is based on weak dependence that arises because
  the forecast errors are a function of a finite number of consecutive
  weakly dependent observations.  But using a fixed window introduces
  another source of dependence: all of the forecasts depend on the
  same coefficient estimates and the estimation uncertainty introduced
  by those estimates does not vanish asymptotically when $R$ is bounded.  One can
  prove that their results apply to fixed window forecasts by using a
  coupling argument similar to \citepos{Cal:11}.  Interested readers
  should refer to \citet{Cal:11} for the argument and to
  \citet{MeP:02} for a review of the necessary coupling results.
  Theorem~\ref{res:1} can be shown to hold when $\hat y_{1t}$ is
  estimated with a fixed-length fixed window using the same arguments.
\end{rem}

Since most empirical papers study more than one alternative model,
Theorem~\ref{sec:1} is of limited use on its own.\footnote{Moreover,
  we would need to account for the existence of multiple models even if
each paper only considered a single model, since there are many papers
studying the same data.}  It can, however, be
used as the basis for a procedure that allows researchers to make
multiple comparisons.  Before presenting a theoretical result, I will
discuss some issues related to multiple hypothesis testing.

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:12b}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.}  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though these papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:12b} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see conclusion~\ref{it:1} of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and this procedure can control \sfwe\ as long as there is a
consistent estimator of that distribution.

@@

This procedure exploits the fact that $R$ is finite in
Theorem~\ref{res:1} and that the expected block length will grow with
$T$.  Under these asymptotics, a growing proportion of the
rolling-window forecasts are the same if we bootstrap the forecasts as
if we bootstrap the empirical data and reestimate the models.
Bootstrapping the forecasts makes the computations faster and easier,
but requires us to drop the first $R$ observations from the bootstrap
(the alternative forecasts are not defined for the first $R$
observations).  I add those observations to the beginning of each
bootstrap sample so that population means under the bootstrap-induced
probability distribution equal sample means.\footnote{This equality is
  strictly true only for the stationary and circular block
  bootstraps.}  The benchmark model still needs to be reestimated in
each bootstrap sample.

@@

\begin{thm}\label{res:2}
  Suppose the conditions of Theorem~\ref{res:1} hold, with assumptions
  on the alternative model, $\hat{y}_{1t}$, holding for each of the
  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$ and let the subscript
  $l$ denote the different quantities associated with $\hat{y}_{lt}$
  (i.e. $\mathcal{F}_{lt}$, etc.)  Also assume that the long-run
  variance-covariance matrix of the vector
  $(\bar{f}_1(\btrue),\dots,\bar{f}_m(\btrue))'$ is uniformly
  positive definite.
